Low field depolarization of dense NV centers ensemble: application to magnetometry

### 2022-10-17 Manuscrit Thèse/chapter 4/Chapter 4.tex
tutu

In the low magnetic field regime however, we have to consider the new eigenstates $\ket{+}$ and $\ket{-}$ and the two-qubits states $\ket{0, \pm}$ and $\ket{\mp, 0}$. These terms are still not fully resonant because of the splitting between the $\ket{+}$ and $\ket{-}$ states caused by the local electric field, but they are close enough in energy that the double flip processes are not entirely quenched.

@@

These two metrics, $\Delta \nu$ and $\abs{\bra{3}\ket{+}}^2$ are what we are interested in for the experiment: we want to increase $\Delta \nu$ to the point where the double flips are completely quenched, but we want $\abs{\bra{3}\ket{+}}^2$ to remain close to 1 in order to preserve the eigenbasis and $T_2^*$ contribution. Based on the plots in Fig.\ref{eigenstates transverse field}-b), the region with $B_\perp \in$ [100 G,200 G] seems to satisfy both these criteria: $\Delta \nu\,(100\ \rm G) \approx 30\ \rm MHz \gg \gamma_f$\footnote{Technically, we want to compare $\Delta \nu$ with the dipole-dipole interaction width $2\gamma_f+\Gamma_{NV}+\Gamma_f$ which we measured to be $\Gamma=8.8\ \rm MHz$ in Fig. [REF].} and $\abs{\bra{3}\ket{+}}^2\, (200\ \rm G) \approx 0.96$.

>>>>

In the low magnetic field regime however, we have to consider the new eigenstates $\ket{+}$ and $\ket{-}$ and the two-qubits states $\ket{0, \pm}$ and $\ket{\mp, 0}$. These terms are still not fully resonant because of the splitting between the $\ket{+}$ and $\ket{-}$ states caused by the local electric field, but they are close enough in energy that the double flip processes are not entirely suppressed.

@@

These two metrics, $\Delta \nu$ and $\abs{\bra{3}\ket{+}}^2$ are the relevant parameters of the experiment: the goal is to increase $\Delta \nu$ to the point where the double flips are completely suppressed, while $\abs{\bra{3}\ket{+}}^2$ remains close to 1 in order to preserve the eigenbasis and $T_2^*$ contribution. Based on the plots in Fig.\ref{eigenstates transverse field}-b), the region with $B_\perp \in$ [100 G,200 G] seems to satisfy both these criteria: $\Delta \nu\,(100\ \rm G) \approx 30\ \rm MHz \gg \gamma_f$\footnote{Technically, $\Delta \nu$ is to be compared with the dipole-dipole interaction width $2\gamma_f+\Gamma_{NV}+\Gamma_f$ which we measured to be $\Gamma=8.8\ \rm MHz$ in Fig. [REF].} and $\abs{\bra{3}\ket{+}}^2\, (200\ \rm G) \approx 0.96$.

### 2022-10-17 Talks/Talk Stuttgart/presentation.tex
tutu

\title{Dipolar interactions in dense ensembles of Nitrogen-Vacancy centers}
\author{Clément Pellet-Mary, Maxime Perdriat, Gabriel Hétet}
\date{Nano-optics group}

@@

\section{Cross-relaxation with NV centers}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_CR_adamas}
\end{frame}
\section{The NV-fluctuator model and experimental verification}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

@@

\section{Dipole-dipole interaction under low magnetic field}

\section{Charcterization of the low field depolarization magnetometry protocol}

>>>>

\title{Low field depolarization of dense NV centers ensemble: application to magnetometry}
\author{Clément Pellet-Mary, Maxime Perdriat, Paul Huillery,\\ Gabriel Hétet}
\date{Nano-optics group}

@@

\section{Cross-relaxation with NV centers}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_CR_adamas}
\end{frame}
\section{The NV-fluctuator model and experimental verification}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

@@

\section{Dipole-dipole interaction under low magnetic field}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_T1_PL_100}
\end{frame}

\begin{frame}{Experiment: $\vec B \perp [111]$}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_champs_transverse}
\end{frame}

\begin{frame}{Summary of the experimental observations}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{shema_summary_exp}
\end{frame}

\section{Low field depolarization magnetometry (LFDM)}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_principle_LFDM}
\end{frame}

\begin{frame}{Sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_sensi_LFDM}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_comparison_litterature}
\end{frame}

\begin{frame}{Comparison with CW ODMR}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_comparison_microwave}
\end{frame}

\begin{frame}{Angular sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_angular_sensitivity}
\end{frame}

\begin{frame}{Application: wide-field magnetometry on irregular surfaces}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_applications_wide_field}
\end{frame}

\begin{frame}{Other applications}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_application_autre}
\end{frame}

\begin{frame}{Take home messages}
\begin{itemize}
\item The spin depolarization in dense NV ensemble is dominated by dipole-dipole interaction with fast decaying centers (fluctuators).
\medskip
\item The leading cause of depolarization in zero field is the spectral overlap of the NV classes, followed by the double flips.
\medskip
\item Low field depolarization magnetometry achieves a sensitivity $\sim 6\ \mu\rm T \cdot \mu \rm m^{3/2} / Hz^{1/2}$ with commercial samples.
\medskip
\item LFDM can be used with powder or polycristalline samples.
\end{itemize}

\end{frame}
